Red Wine Quality by Fahad Alhajjaj
========================================================
###Citation Request:  
This dataset is public available for research.  
The details are described in [Cortez et al., 2009].  
Please include this citation if you plan to use this database:  
  
P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis.  
Modeling wine preferences by data mining from physicochemical properties.  
In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.  

Available at:  
[Elsevier](http://dx.doi.org/10.1016/j.dss.2009.05.016)  
[Pre-press (pdf)](http://www3.dsi.uminho.pt/pcortez/winequality09.pdf)  
[bib](http://www3.dsi.uminho.pt/pcortez/dss09.bib)  
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      warning=FALSE,
                      message=FALSE,
                      fig.width=12,
                      fig.height=8)
```

```{r packages}
library(ggplot2)
library(gridExtra)
library(knitr)
library(GGally)
```

```{r Load_the_Data}
# Load the Data
red_wine <- read.csv("wineQualityReds.csv")
 # droping the first column which is an index of the instances
red_wine$X <- NULL

#Changing the quality values to letters to better visualize the quality
red_wine$quality.class <- chartr('0123456789', 'KJIHGFEDCB', red_wine$quality)
```

In this report a dataset of 1599 red wine instances, each with 12 vriables  
discribing the instance, is to be explored. A list of the 12 variables:  
  1. fixed acidity (tartaric acid - g / dm^3)  
  2. volatile acidity (acetic acid - g / dm^3)  
  3. citric acid (g / dm^3)  
  4. residual sugar (g / dm^3)  
  5. chlorides (sodium chloride - g / dm^3)  
  6. free sulfur dioxide (mg / dm^3)  
  7. total sulfur dioxide (mg / dm^3)  
  8. density (g / cm^3)  
  9. pH  
 10. sulphates (potassium sulphate - g / dm3)  
 11. alcohol (% by volume)  
 12. quality (score between 0 and 10)  

# Univariate Plots Section

```{r Summary_of_the_variables}
dim(red_wine)
str(red_wine)
summary(red_wine)
```

The dataset has 1599 observation with 12 discribtive variables.  
This a statestical summary of all variables is shown above and will be used  
as referance and to understand the variables better

```{r Univariate_Plots_1, }
p1 <- ggplot(aes(x = fixed.acidity), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.1) +
  xlab('Fixed Acidity') +
  ylab('Count') +
  ggtitle('Fixed Acidity Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

p2 <- ggplot(aes(x = volatile.acidity), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.01) +
  xlab('Volatile Acidity') +
  ylab('Count') +
  ggtitle('Volatile Acidity Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

grid.arrange(p1, p2, ncol = 1)
```

We see in the above histograms:  
Fixed acidity has a normal distribution with a median 7.90 and a mean 8.32.  
Volatile Acidity has a normal distribution with median 0.5200 and mean 0.5278.  
The x-axis is different in both histograms due to the quantity of the two acids.

```{r Univariate_Plots_2}
ggplot(aes(x = citric.acid), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.01) +
  xlab('Citric Acid') +
  ylab('Count') +
  ggtitle('Citric Acid Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see in the above histogram Citric Acid has two long bins at 0 and at 0.48  
Also, Citric Acid has a median 0.260 and a mean 0.271.  

```{r Univariate_Plots_3}
ggplot(aes(x = residual.sugar), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.1) +
  scale_x_log10() +
  xlab('Residual Sugar') +
  ylab('Count') +
  ggtitle('Residual Sugar Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

```

We see in the above histogram for Residual Sugar has long tail due to outliers.  
The Residual Sugar has a median 2.200 and a mean 2.539  

```{r Univariate_Plots_4}
p3 <- ggplot(aes(x = chlorides), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.001) +
  xlab('Chlorides') +
  ylab('Count') +
  ggtitle('Chlorides Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

p4 <- ggplot(aes(x = chlorides), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.001) +
  coord_cartesian(xlim = c(0.025, 0.125)) +
  xlab('Chlorides') +
  ylab('Count') +
  ggtitle('Chlorides Histogram - with limited x-axis') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

grid.arrange(p3, p4, ncol = 1)
```

In the above Chlorides Histogram we zoomed in to better understand the graph.  
Chlorides Histogram has long tail due to outliers.  
The Chlorides has a median 0.07900 and a mean 0.08747  

```{r Univariate_Plots_5}
ggplot(aes(x = free.sulfur.dioxide), data = red_wine) +
  geom_histogram(fill = 'orange', binwidth = 1) +
  xlab('Free Sulfur Dioxide') +
  ylab('Count') +
  ggtitle('Free Sulfur Dioxide Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

ggplot(aes(x = total.sulfur.dioxide), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 1) +
  xlab('Total Sulfur Dioxide') +
  ylab('Count') +
  ggtitle('Total Sulfur Dioxide Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

ggplot() +
  geom_histogram(aes(x = free.sulfur.dioxide),
                 data = red_wine,
                 fill = 'orange',
                 binwidth = 1) +
  
  geom_histogram(aes(x = total.sulfur.dioxide),
                 data = red_wine,
                 fill = 'blue',
                 binwidth = 1) +
  
  xlab('Free and Total Sulfur Dioxide') +
  ylab('Count') +
  ggtitle('Free and Total Sulfur Dioxide Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

In the above histograms we started with the Free Sulfur Dioxide Histogram,  
then we did the Total Sulfur Dioxide Histogram, then we combined them togather  
since the Free Sulfur Dioxide is part of the Total Sulfur Dioxide.  
We noticed that the Free Sulfur Dioxide is mostly in the low levels of the gas.  
The Free Sulfur Dioxide has a median 14.00 and a mean 15.87.  
The Total Sulfur Dioxide has a median 38.00 and a mean 46.47.   

```{r Univariate_Plots_6}
ggplot(aes(x = density), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.0001) +
  xlab('Density') +
  ylab('Count') +
  ggtitle('Density Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

In the above Density Histogram, Density has a normal distribution  
with median 0.9968 and mean 0.9967.  

```{r Univariate_Plots_7}
ggplot(aes(x = pH), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.01) +
  xlab('pH') +
  ylab('Count') +
  ggtitle('pH Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

In the above pH Histogram, pH has a normal distribution  
with median 3.310 and mean 3.311.   

```{r Univariate_Plots_8}
ggplot(aes(x = sulphates), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.01) +
  xlab('Sulphates') +
  ylab('Count') +
  ggtitle('Sulphates Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see in the above histogram for Sulphates has long tail due to outliers.  
The Sulphates has a median 0.6200 and a mean 0.6581. 

```{r Univariate_Plots_9}
ggplot(aes(x = alcohol), data = red_wine) +
  geom_histogram(fill = 'blue', binwidth = 0.1) +
  xlab('Alcohol') +
  ylab('Count') +
  ggtitle('Alcohol Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see in the above histogram for Alcohol has a Positively-skewed distribution.  
The Alcohol has a median of 10.20 and a mean of 10.42.  

```{r Univariate_Plots_10}
ggplot(aes(x = quality.class), data = red_wine) +
  geom_bar(color = 'black', fill = 'blue') +
  xlab('Quality') +
  ylab('Count') +
  ggtitle('Quality Histogram') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see in the above histogram for Quality normal distribution.  
The Quality has a median of 6.000 and a mean of 5.636.  
We see most wines score a 5 or 6 in quality.  

# Univariate Analysis

### What is the structure of your dataset?
There is 1599 red wine instances with 12 features:  
(fixed.acidity, volatile.acidity, citric.acid, residual.sugar, chlorides,  
free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol,  
quality). There is only one ordered variable, quality and quality.class.  

(worst score) -----------> (best score)  
    0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10  
    K, J, I, H, G, F, E, D, C, B, A  
  
Other observations:  
* All wine instances score between 3 and 8.  
* Both Residual Sugar and Chlorides have long tails.  
* Minumum Alcohol % is 8.40 and Maximum Alcohol % is 14.90  

### What is/are the main feature(s) of interest in your dataset?
The main features of interest in the dataset are fixed acidity and quality.  
I'd like to see how the other variables effect the these two features.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
All other variables would help. Density and pH would have the a relation with  
fixed acidity. The fixed acidity, volatile.acidity, alcohol would have the  
most effect on quality.  

### Did you create any new variables from existing variables in the dataset?
No.  

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?  
Residual Sugar and Chlorides have long tails when I graphed them.  
I zoomed in when I plot Chlorides Histogram to better understand the graph  
because it had a long tail.  

I applied some a transformation on the Residual Sugar it is heavily right skewed.  
I took my reviewer advice on this matter.

I added a new variable called 'quality.class', I converted quality scale to  
quality class by converting numbers (0 to 10) to letters (A - K) to better  
understand and visualies the quality.

# Bivariate Plots Section

```{r Bivariate_Plots_1}
ggpairs(data = red_wine,
        lower = list(continuous = wrap(ggally_points,
                                       size = 0.75,
                                       color = "blue",
                                       alpha = 0.05)))
```

This is an overview of the Bivaritate plots. It is used to better choose the  
graphs and to understand the relationship between variables.

```{r Bivariate_Plots_2}
ggplot(aes(x = fixed.acidity, y = citric.acid), data = red_wine) +
  geom_point(color = 'red',
             alpha = 0.50) +
  stat_smooth(method= 'lm', color = 'blue') +
  xlab('Fixed Acidity') +
  ylab('Citric Acid') +
  ggtitle('Fixed Acidity vs. Citric Acid') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$fixed.acidity, red_wine$citric.acid)
```

We see a positive correlation between Fixed Acidity and Citric Acid.  
The Pearson's product-moment correlation is 0.6717034.

```{r Bivariate_Plots_3}
ggplot(aes(x = fixed.acidity, y = density), data = red_wine) +
  geom_point(color = 'red',
             alpha = 0.50) +
  xlab('Fixed Acidity') +
  ylab('Density') +
  ggtitle('Fixed Acidity vs. Density') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$fixed.acidity, red_wine$density)
```

We see a positive correlation between Fixed Acidity and Density.  
The Pearson's product-moment correlation is 0.6680473.  

```{r Bivariate_Plots_4}
ggplot(aes(x = fixed.acidity, y = pH), data = red_wine) +
  geom_point(color = 'red',
             alpha = 0.50) +
  xlab('Fixed Acidity') +
  ylab('pH') +
  ggtitle('Fixed Acidity vs. pH') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$fixed.acidity, red_wine$pH)
```

We see a negative correlation between Fixed Acidity and pH.  
The Pearson's product-moment correlation is -0.6829782.

```{r Bivariate_Plots_5}
ggplot(aes(x = fixed.acidity, y = alcohol), data = red_wine) +
  geom_point(color = 'red',
             alpha = 0.50) +
  xlab('Fixed Acidity') +
  ylab('Alcohol') +
  ggtitle('Fixed Acidity vs. Alcohol') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$fixed.acidity, red_wine$alcohol)
```

We see almost no correlation between Fixed Acidity and Alcohol.  
The Pearson's product-moment correlation is -0.06166827.

```{r Bivariate_Plots_6}
ggplot(aes(x = volatile.acidity, y = citric.acid), data = red_wine) +
  geom_point(color = 'red',
             alpha = 0.50) +
  xlab('Volatile Acidity') +
  ylab('Citric Acid') +
  ggtitle('Volatile Acidity vs. Citric Acid') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$volatile.acidity, red_wine$citric.acid)
```

On the other hand, We see a negative correlation between Volatile Acidity and  
Citric Acid. The Pearson's product-moment correlation is -0.5524957.  

```{r Bivariate_Plots_7}
ggplot(aes(x = quality.class, y = alcohol), data = red_wine) +
  geom_boxplot() + 
  xlab('Quality') +
  ylab('Alcohol') +
  ggtitle('Quality vs. Alcohol') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$quality, red_wine$alcohol)
```

We see a positive correlation between Quality and Alcohol.  
The Pearson's product-moment correlation is 0.4761663.  

```{r Bivariate_Plots_8}
ggplot(aes(x = quality.class, y = volatile.acidity), data = red_wine) +
  geom_boxplot() + 
  xlab('Quality') +
  ylab('Volatile Acidity') +
  ggtitle('Quality vs. Volatile Acidity') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$quality, red_wine$volatile.acidity)
```

We see some negative correlation between Quality and Volatile Acidity  
The Pearson's product-moment correlation is -0.3905578.

```{r Bivariate_Plots_9}
ggplot(aes(x = quality.class, y = pH), data = red_wine) +
  geom_boxplot() +
  xlab('Quality') +
  ylab('pH') +
  ggtitle('Quality vs. pH') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$quality, red_wine$pH)
```

We almost see no correlation between Quality and pH  
The Pearson's product-moment correlation is -0.05773139.  

```{r Bivariate_Plots_10}
ggplot(aes(x = quality.class, y = fixed.acidity), data = red_wine) +
  geom_boxplot() + 
  xlab('Quality') +
  ylab('Fixed Acidity') +
  ggtitle('Quality vs. Fixed Acidity') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

cor.test(red_wine$quality, red_wine$fixed.acidity)
```

We almost see no correlation between Quality and Fixed Acidity  
The Pearson's product-moment correlation is 0.1240516.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?  
We saw some positive, negative and no correlation between the features of  
interest and other features.  

We saw positive correlations between:  
Fixed Acidity and Citric Acid  
Fixed Acidity and Density
Quality and Alcohol

We saw negative correlations between:  
Fixed Acidity and pH  
Volatile Acidity and Citric Acid  
Quality and Volatile Acidity  

We saw no correlations between:  
Fixed Acidity and Alcohol.  
Quality and pH

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
Yes, We see a negative correlation between Volatile Acidity and
Citric Acid. The Pearson?s product-moment correlation is -0.5524957.  
That was interesting.

### What was the strongest relationship you found?
There was three strong relationships in the dataset:  
Fixed Acidity and Citric Acid (positive relation - pearson's correlation = 0.67)  
Fixed Acidity and Density (positive relation - pearson's correlation = 0.67)  
Fixed Acidity and pH (negative relation - pearson's correlation =  -0.68)  

# Multivariate Plots Section

```{r Multivariate_Plots_1}
ggplot(aes(x = fixed.acidity, y = alcohol), data = red_wine) + 
  geom_point(aes(color = quality.class),
             size = 2) +
  scale_color_brewer(type = 'div',
                     palette = "RdYlBu",
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  xlab('Fixed Acidity') +
  ylab('Alcohol') +
  ggtitle('Fixed Acidity vs. Alcohol') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see some positive coorelation with consentration in low values of x and y.
We also see that quality wine gets better as the x and y values increases.

```{r Multivariate_Plots_2}
ggplot(aes(x = fixed.acidity, y = pH), data = red_wine) + 
  geom_point(aes(color = quality.class),
             size = 2) +
  scale_color_brewer(type = 'div',
                     palette = 'RdYlBu',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  xlab('Fixed Acidity') +
  ylab('pH') +
  ggtitle('Fixed Acidity vs. pH') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We are see some negative coorelation between Fixed Acidity vs. pH  
We also quality is scttered all over the graph.

```{r Multivariate_Plots_3}
ggplot(aes(x = fixed.acidity, y = density), data = red_wine) +
  geom_point(aes(color = quality.class),
             size = 2) +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  xlab('Fixed Acidity') +
  ylab('Density') +
  ggtitle('Fixed Acidity vs. Density') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We see a positive correlation between Fixed Acidity and Density.  
We mostly see the higher guality wines are lower than the lower quality wine.

```{r Multivariate_Plots_4}
ggplot(aes(x = fixed.acidity, y = citric.acid),
       data = red_wine) + 
  geom_point(aes(color = quality.class),
             size = 2) +
  scale_color_brewer(type = 'div',
                     palette = 'RdYlBu',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  xlab('Fixed Acidity') +
  ylab('Citric Acid') +
  ggtitle('Fixed Acidity vs. Citric Acid') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

We some positive correlation between Fixed Acidity/Volatile Acidity and  
Citric Acid. Also, we can see some overlabing in the lower x and y values.
We also see that quality wine gets better as the x and y values increases.

```{r Multivariate_Plots_5}
ggplot(aes(x = quality.class, y = fixed.acidity/volatile.acidity),
       data = red_wine) + 
  geom_boxplot() +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  xlab('Quality') +
  ylab('Fixed Acidity/Volatile Acidity') +
  ggtitle('Fixed Acidity/Volatile Acidity vs. Quality') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
```

The lower the quality the smaller the quantile boxes.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?  
There was no relation between Fixed Acidity and Alcohol. However, when we  
plotted the ration of Fixed Acidity over Volatile Acidity and Alcohol  
we saw a positive coorelation.

### Were there any interesting or surprising interactions between features?
Yes, the ration of Fixed Acidity over Volatile Acidity has some intersting  
results when plotted with other features.  

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r Plot_One}
ggplot(aes(x = fixed.acidity, y = citric.acid), data = red_wine) +
  geom_point(aes(color = quality.class),
             size = 3) +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  coord_cartesian(xlim= c(min(red_wine$fixed.acidity),
                          quantile(red_wine$fixed.acidity, 0.99))) +
  stat_smooth(method= 'lm', color = 'red') +
  xlab('Fixed Acidity (g/dm^3)') +
  ylab('Citric Acid (g/dm^3)') +
  ggtitle('Fixed Acidity vs. Citric Acid vs. Quality') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))
print('Fixed Acidity (g/dm^3) Statistics')
summary(red_wine$fixed.acidity)

print('Citric Acid (g/dm^3) Statistics')
summary(red_wine$citric.acid)

print('Quality Statistics')
summary(red_wine$quality)
cor.test(red_wine$fixed.acidity, red_wine$citric.acid)
```

### Description One  
We see a positive correlation between Fixed Acidity and Citric Acid.  
The Pearson's product-moment correlation is 0.6717034.
Most of the higher quality wines (C-D) are above the regression line while  
the lower quality (G-H) are below the regression line. However, quality wine   
(E-F) are above and below the regression line. The points are scattered evenly  
through the graph. I chose this graph because I wanted to see how the quality  
is scattered in this graph. I was not surprised when I saw how quality was
scattered in the graph. I droped the top 1 % of Fixed Acidity data because there  
was some gaps in the values. 

### Plot Two
```{r Plot_Two}
ggplot(aes(x = fixed.acidity, y = density), data = red_wine) +
  geom_point(aes(color = quality.class),
             size = 3) +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  coord_cartesian(xlim= c(min(red_wine$fixed.acidity),
                          quantile(red_wine$fixed.acidity, 0.99))) +
  stat_smooth(method= 'lm', color = 'red') +
  xlab('Fixed Acidity (g/dm^3)') +
  ylab('Density (g/cm^3)') +
  ggtitle('Fixed Acidity vs. Density vs. Quality') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

print('Fixed Acidity (g/dm^3) Statistics')
summary(red_wine$fixed.acidity)

print('Density (g/cm^3) Statistics')
summary(red_wine$density)

print('Quality Statistics')
summary(red_wine$quality)
cor.test(red_wine$fixed.acidity, red_wine$density)
```

### Description Two
We see a positive correlation between Fixed Acidity and Density.  
The Pearson's product-moment correlation is 0.6680473.  
Most of the higher quality wines (C-D) are below the regression line while  
the lower quality (G-H) are along the regression line. However, quality wine   
(E-F) are above and below the regression line where (F) is mostly above the line.  
The points are scattered nicely in the graph. I chose this graph because   
I wanted to see how the quality is scattered in this graph. I was not surprised  
when I saw how quality was scattered in the graph. I droped the top 1 % of Fixed  
Acidity data because there was some gaps in the values. 

### Plot Three
```{r Plot_Three}
ggplot(aes(x = fixed.acidity, y = alcohol), data = red_wine) + 
  geom_point(aes(color = quality.class),
             size = 3) +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality',
                                          reverse = FALSE,
                                          override.aes = list(alpha = 1,
                                                              size = 2))) +
  theme_dark() +
  coord_cartesian(xlim= c(min(red_wine$fixed.acidity),
                          quantile(red_wine$fixed.acidity, 0.99))) +
  stat_smooth(method= 'lm', color = 'red') +
  xlab('Fixed Acidity (g/dm^3)') +
  ylab('Alcohol (% by volume)') +
  ggtitle('Fixed Acidity vs. Alcohol vs. Quality') +
  theme(plot.title = element_text(size = 20, hjust = 0.5))

print('Fixed Acidity (g/dm^3) Statistics')
summary(red_wine$fixed.acidity)

print('Alcohol (% by volume) Statistics')
summary(red_wine$alcohol)

print('Quality Statistics')
summary(red_wine$quality)
cor.test(red_wine$fixed.acidity, red_wine$alcohol)

```

### Description Three
We see almost no correlation between Fixed Acidity and Alcohol.  
The Pearson's product-moment correlation is -0.06166827.  
Most of the higher quality wines (C-D) are above the regression line while  
the lower quality (F-H) are below the regression line. Quality wine (E), on the   
other hand, is scattered everywhere. The points are scattered nicely in the graph.  
I chose this graph because I was fascinated by how alcohol has an effect on quality  
I was surprised when I saw how quality was scattered in the graph. I did some  
limitiation on the x-axis by taking out the top 1% of the values.  

------
# Reflection
I this project I worked on Red Wine Quality dataset.  
The dataset has 1599 observations and 12 variables. I started by including a  
new variable for quality class (A - K) converted from quality measure (0-10).  
Then I started to examin each variable to better understand the dataset.  

There was some coorelation between variables, some were positive and some were  
negative. Some relations were obviouse, such as Fixed Acidity and pH, and some  
were surprising to me, such as Fixed Acidity and Alcohol.  

Some limition in the dataset were the number of observations.  
The more observations we have the better understanding and exploration of the  
dataset. To explore the dataset further, I would try and find the realstionship  
between all features and the quality feature to be able to predict the quality  
of a specific wine.  